Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-07-11 inspiral_svd.tex
lloid_paper: incorporate Larry's (minor) comments and acknowledge him
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1269 ccdd05d5-56c1-461a-bf98-85f6876523b4
"may" --> "might" x1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1287 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{abstract}
Rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts for the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
filtering strategy that could produce early-warning triggers before
gravitational radiation from the final merger has arrived at the detectors.
\end{abstract}

@@

\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection,
Patrick Brady for countless fruitful conversations about
low latency analysis methods, and John Zweizig for
disscussions about \LIGO\ data acquisition.  NF would like to thank Alessandra
Corsi for illuminating discussions on astronomical motivations.  This research
is supported by the National Science Foundation through a Graduate Research
Fellowship to LS and by the Perimeter Institute for Theoretical Physics through
a fellowship to CH. DK is supported from the Max Planck Gesellschaft.

>>>>

\begin{abstract}
Rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts for the astronomical
community might make it possible to observe the onset of electromagnetic
emission from compact binary coalescence.  We demonstrate a computationally
practical filtering strategy that could produce early-warning triggers before
gravitational radiation from the final merger has arrived at the detectors.
\end{abstract}

@@

\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection,
Patrick Brady for countless fruitful conversations about
low latency analysis methods, and John Zweizig for
disscussions about \LIGO\ data acquisition.  NF would like to thank Alessandra
Corsi and Larry Price for illuminating discussions on astronomical motivations.
This research
is supported by the National Science Foundation through a Graduate Research
Fellowship to LS and by the Perimeter Institute for Theoretical Physics through
a fellowship to CH. DK is supported from the Max Planck Gesellschaft.
